---
title: "treatment"
author: "DAHEE"
date: "12/7/2017"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(tidyverse)
library(stringr)
library(tableone)
library(mlr)
library(mi)
load("/Users/daheelee/Desktop/lhs_2/36361-0001-Data.rda")
```
#Include other variable (seeing a doctor)
```{r}
doctor= da36361.0001 %>%
  select(CATAG3,ADWRDLOT) %>%
  rename(age= CATAG3, suiThink=ADWRDLOT) %>% 
  mutate_if(is.character, as.factor)

head(doctor)
```
#Coding
```{r}

doctor_coding = doctor %>% 
  mutate(age = case_when (age == '(1) 12-17 Years Old'~1,
                          age == '(2) 18-25 Years Old'~2,
                          age == '(3) 26-34 Years Old'~3,
                          age == '(4) 35-49 Years Old'~4,
                          age == '(5) 50 or Older'~5))%>% 
   mutate(suiThink = case_when (suiThink == '(1) Yes'~'y',
                          suiThink == '(2) No'~'n')) 
 

doctor_adult=doctor_coding %>% 
  filter(age>2) %>% 
  select(age, suiThink) 


head(doctor_adult)
doctor_na = doctor_adult%>% 
  filter(!is.na(suiThink))

doctor_na %>% 
  missing_data.frame()

```

## convert to factor &  Create dummy variables
```{r}
dummy_doctor=doctor_na %>% 
  mutate_if(is.character, as.factor) %>% 
    createDummyFeatures()

dummy_doctor = dummy_doctor %>% select(-suiThink.n)
dummy_doctor$suiThink.y = as.factor(dummy_doctor$suiThink.y)

```
## Split the data in train and test
```{r}
set.seed(1)

n <- nrow(dummy_doctor)
shuffled <- dummy_doctor[sample(n),]


train_doctor <- shuffled[1:round(0.7 * n),]
test_doctor <- shuffled[(round(0.7 * n) + 1):n,]


```
#Assign the task
```{r}
train_task_doctor = makeClassifTask(data = train_doctor,
                             target = 'suiThink.y',
                             positive = 1)


```
#Resampling
```{r}
lrn_doctor = makeLearner('classif.naiveBayes', predict.type='prob')
resample_method = makeResampleDesc('CV',  iters = 3)
set.seed(1000)
resample_performance_doctor = resample(learner = lrn_doctor,
                                task = train_task_doctor,
                                resampling = resample_method,
                                measures = list(acc, auc, ppv, tpr))
resample_performance_doctor$measures.test
```
# Visualization 
```{r}
d = generateThreshVsPerfData(resample_performance_doctor, measures = list(fpr, fnr, mmce))


plotThreshVsPerf(d)
```


#prepare the data
##seclect variable
1)predictive variable : age, sex, tobacco, alcohol, marijuana, cocaine, employment, education, decreased appetite, increased appetite
2)outcome : think about Suicide, suicide would be better, commit suicide, plan suicide
```{r}

dataset= da36361.0001 %>%
  select(CATAG3, IRSEX, CIGEVER, ALCEVER, MJEVER, COCEVER, JBSTATR2, EDUCCAT2, ADWRELES, ADWREMOR, ADWRDLOT, ADWRDBTR, ADWRSTHK, ADWRSPLN, ADWRSATP) %>%
  rename(age= CATAG3, sex=IRSEX, tobacco=CIGEVER, alcohol=ALCEVER, marijuana= MJEVER, cocaine= COCEVER, job=JBSTATR2, education=EDUCCAT2, eatingSmall = ADWRELES, eatingLarge= ADWREMOR,  suiThink=ADWRDLOT) %>% 
  mutate_if(is.character, as.factor)

nrow(da36361.0001)
```
## Coding variable, only adult, suicide(even think)
I recode the variable name readable
```{r}

data_coding = dataset %>% 
  mutate(age = case_when (age == '(1) 12-17 Years Old'~1,
                          age == '(2) 18-25 Years Old'~2,
                          age == '(3) 26-34 Years Old'~3,
                          age == '(4) 35-49 Years Old'~4,
                          age == '(5) 50 or Older'~5))%>% 
  mutate(sex = case_when (sex == '(1) Male'~ 'm',
                          sex == '(2) Female'~'f'))%>% 
  mutate(tobacco = case_when (tobacco == '(1) Yes'~'y',
                          tobacco == '(2) No'~'n')) %>% 
  mutate(alcohol = case_when (alcohol == '(1) Yes'~'y',
                          alcohol == '(2) No'~'n')) %>% 
  mutate(marijuana = case_when (marijuana == '(1) Yes'~'y',
                          marijuana == '(2) No'~'n')) %>% 
  mutate(cocaine = case_when (cocaine == '(1) Yes'~'y',
                          cocaine == '(2) No'~'n')) %>% 
  mutate(job = case_when (job == "(01) Worked at full-time job, past week"~'full',
                          job == "(02) Worked at part time job, past week"~'part',
                          job == "(3) Some college (IREDUC2=9-10 and AGE2>=7)"~'some',
                          job == "(04) Unemployed/on layoff, looking for work"~'unemployed',
                          job == "(05) Disabled"~'disabled',
                          job == "(06) Keeping house full-time"~'house',
                          job == "(07) In school/training"~'school',
                          job == "(08) Retired"~'retired')) %>%
  mutate(education = case_when (education == "(1) Less than high school (IREDUC2<=7 and AGE2>=7)"~'<high',
                          education == "(2) High school graduate (IREDUC2=8 and AGE2>=7)"~'high',
                          education == "(3) Some college (IREDUC2=9-10 and AGE2>=7)"~'some',
                          education == "(4) College graduate (IREDUC2=11 and AGE2>=7)"~'gradutate',
                          education == "(5) 12 to 17 year olds (AGE2<=6)"~'12-17yr')) %>% 
  mutate(eatingSmall = case_when (eatingSmall == '(1) Yes'~'y',
                          eatingSmall == '(2) No'~'n')) %>% 
  mutate(eatingLarge = case_when (eatingLarge == '(1) Yes'~'y',
                          eatingLarge == '(2) No'~'n')) %>% 
  mutate(suiThink = case_when (suiThink == '(1) Yes'~'y',
                          suiThink == '(2) No'~'n')) 
  
```
## count outcome variable
1) I expect that the number of planning suicide would not many. I checked it. I got 6513 data available, which is good enough. 
```{r}
data_coding %>% 
  group_by(suiThink) %>% 
  count()
```

##Select adult 
1) in our dataset, they consider adult as above 26 years old. So, I only select those above '2' which is '(2) 18-25 Years Old'.
```{r}
adult=data_coding %>% 
  filter(age>2) %>% 
  select(age, sex, tobacco, alcohol,marijuana, cocaine, job, education, eatingSmall, eatingLarge, suiThink) 


adult= adult%>% 
  filter(!is.na(suiThink))
```
## Missingness of the data
####simple count
```{r}
age= sum(is.na(adult$age))
sex= sum(is.na(adult$sex))
tobacco=sum(is.na(adult$tobacco))
alcohol=sum(is.na(adult$alcohol))
marijuana=sum(is.na(adult$marijuana))
cocaine=sum(is.na(adult$cocaine))
job=sum(is.na(adult$job))
education=sum(is.na(adult$education))
eatingSmall=sum(is.na(adult$eatingSmall))
eatingLarge=sum(is.na(adult$eatingLarge))
suiThink=sum(is.na(adult$suiThink))

num_missing= data.frame(age, sex, tobacco, alcohol, marijuana,cocaine, job, education, eatingSmall,eatingLarge, suiThink )
num_missing

nrow(adult)
```
##Analyze missingness
cocain, marijuana, cocain, eatingSmall and eatingLarge have missing variables. I use CreateTableOne to see if there is any dependency to other variables
1) We cannot see any dependency in here except eatingLarge
2) It is interesting that the correlation between missingness for eatingLarge and education, eatingSmall and suicide think is statistically significant 

```{r}
adult %>% 
  missing_data.frame()

adult %>%
  mutate(missing=is.na(marijuana)) %>%
  CreateTableOne(strata='missing',data=.) 

adult %>% 
  mutate(missing=is.na(cocaine)) %>%
  CreateTableOne(strata='missing',data=.) 

adult %>% 
  mutate(missing=is.na(job)) %>%
  CreateTableOne(strata='missing',data=.) 

adult %>% 
  mutate(missing=is.na(eatingSmall)) %>%
  CreateTableOne(strata='missing',data=.) 

adult %>% 
  mutate(missing=is.na(eatingLarge)) %>%
  CreateTableOne(strata='missing',data=.) 
```
#Naive-Bayes
##convert to factor &  Create dummy variables
1) proportion of outcome : 0.49 
```{r}
dummy_naive=adult %>% 
  mutate_if(is.character, as.factor) %>% 
    createDummyFeatures()

head(adult)

dummy_naive = dummy_naive %>% select(-suiThink.n)
dummy_naive$suiThink.y = as.factor(dummy_naive$suiThink.y)

dummy_naive %>% 
  group_by(suiThink.y) %>% 
  count()
```

# Split the data in train and test
```{r}
set.seed(1)

n <- nrow(dummy_naive)
shuffled <- dummy_naive[sample(n),]


train_naive <- shuffled[1:round(0.7 * n),]
test_naive <- shuffled[(round(0.7 * n) + 1):n,]
```
#Assign the task
```{r}
train_task_naive = makeClassifTask(data = train_naive,
                             target = 'suiThink.y',
                             positive = 1)


```
#Resampling
```{r}
lrn_naive = makeLearner('classif.naiveBayes', predict.type='prob')
resample_method = makeResampleDesc('CV',  iters = 5)
set.seed(1000)
resample_performance_naive = resample(learner = lrn_naive,
                                task = train_task_naive,
                                resampling = resample_method,
                                measures = list(acc, auc, ppv, tpr))
resample_performance_naive$measures.test
```
## Visualization 
```{r}
d = generateThreshVsPerfData(resample_performance_naive, measures = list(fpr, fnr, mmce))


plotThreshVsPerf(d)
```

# ROC curve
```{r}
df = generateThreshVsPerfData(resample_performance_naive, measures = list(fpr, tpr, mmce))
plotROCCurves(df)
```
